### 2018-05-26 intro.tex
Fix two "FIXME"s in the draft
- Citation to BLAS
- List of AArch64 processors with shared L2 cache

\section{Introduction}\label{sec:intro}
Dense linear algebra libraries are the most fundamental software in
scientific and engineering computing domains.
Basic Linear Algebra Subprograms (BLAS) (FIXME) defines a collection
of APIs which act as standard building blocks for dense matrix operations.
BLAS routines are divided into 3 levels,
level-1 for vector-vector operations,
level-2 for matrix-vector operations,
and level-3 for matrix-matrix operations.
Processor vendors often provide BLAS implementations
that are highly optimized for their processors,
such as Intel MKL, AMD ACML and NVIDIA cuBLAS.
The HPC community has also contributed several high-quality
BLAS implementations, e.g., ATLAS~\cite{atlas},
GotoBLAS~\cite{gotoblas}, OpenBLAS~\cite{openblas},
and BLIS~\cite{blis,blisport}.

@@

Following the trend in recent decades, modern architecture design
is introducing more and more cores on a single processor chip.
To reduce cost of on-chip cache memories and coherence networks,
shared caches may become common in future many-core processors.
In addition, non-LRU replacement policies, for example, pseudo-random,
may also be used to further reduce the cache design complexity.
Indeed, some high-performance processors based on the
ARM technology,
have already adopted this design. (FIXME list the processors)
As a result, developing a better solution to reduce
the inter-thread cache conflicts 
for non-LRU shared caches is important.

>>>>

\section{Introduction}\label{sec:intro}
Dense linear algebra libraries are the most fundamental software in
scientific and engineering computing domains.
Basic Linear Algebra Subprograms (BLAS)~\cite{blas}  defines a collection
of APIs which act as standard building blocks for dense matrix operations.
BLAS routines are divided into 3 levels,
level-1 for vector-vector operations,
level-2 for matrix-vector operations,
and level-3 for matrix-matrix operations.
Processor vendors often provide BLAS implementations
that are highly optimized for their processors,
such as Intel MKL, AMD ACML and NVIDIA cuBLAS.
The HPC community has also contributed several high-quality
BLAS implementations, e.g., ATLAS~\cite{atlas},
GotoBLAS~\cite{gotoblas}, OpenBLAS~\cite{openblas},
and BLIS~\cite{blis,blisport}.

@@

Following the trend in recent decades, modern architecture design
is introducing more and more cores on a single processor chip.
To reduce cost of on-chip cache memories and coherence networks,
shared caches may become common in future many-core processors.
In addition, non-LRU replacement policies, for example, pseudo-random,
may also be used to further reduce the cache design complexity.
Indeed, some high-performance processors based on the
ARM technology, e.g., the Phytium processor series~\cite{phytium},
%% I'm sure they have shared L2 caches,
%% but have not found any technical specification about the replacement policy
%% XGene from AppliedMicro~\cite{xgene},
%% ThunderX from Cavium~\cite{thunderx}
have already adopted this design. 
As a result, developing a better solution to reduce
the inter-thread cache conflicts 
for non-LRU shared caches is important.
